Structural Divergence Analysis

### 2017-03-20 analysis-structure.Rmd
cambios 20/3/17

```{r set-my-colors}
# set my colors
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```

@@

```{r-mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

@@

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(mean z.RSD)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

@@

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "mut")
d.strong = subset(d, dataset == "mut+sel")

@@

>>>>

```{r set-my-colors}
# set my colors
myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "no-sel", "strong", "strong-sel")
```

@@

```{r-mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "strong-sel"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-sel"))

@@

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "<zRSDi>") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "no-sel")
p.facet %+% subset(d, dataset == "strong-sel") 
p.facet

@@

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-sel")
d.strong = subset(d, dataset == "strong-sel")

@@

```
```{r structure-profiles-comparison}

# compare profiles
## plot
par(pty = "s")
plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")
plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
plot(x = d.strong$mean.z.RSD, y = CN, xlab = "theoretical with strong selection <zRSDi>")

## calculate corelations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
r.strong.mean.z.RSD.CN = cor(d.strong$mean.z.RSD, CN)

cor.df = data.frame("comparison" = c("exp.mean.z.RSD vs CN", "mut.mean.z.RSD vs CN", "strong.mean.z.RSD vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.strong.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
```
